Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-05-27 Masterarbeit_Robotik_Pamuk.tex
cite

\chapter{Salamander 4}\label{cha:salamander4}
This chapter briefly describes the Salamander 4 operating system by SIGMATEK. Salamander 4 is the proprietary operating system of SIGMATEK. It is based on Linux version 5.15.94 and integrates Xenomai 3.2, a real-time development environment \cite{XenomaiXenomai}. Salamander 4 is a 64-bit system, which refers to the x86\_64 architecture. The real-time behaviour is achieved through the use of Symmetric Multi-Processing (SMP) and Preemptive Scheduling (PREEMPT). In addition, it uses IRQPIPE to process interrupts in a way that meets the real-time requirements of the system. The output of the command \texttt{uname -a} can be observed in code \ref{output:uname_a_virt}.

@@

\clearpage
\section{KVM exit reasons}\label{sec:kvm_exit_reasons}
\subsection{APIC\_WRITE}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/kvm_exit_vapic.png}
	\caption[kvm exits default]{kvm exits default}
	\label{fig:kvm_exit_vapic}
\end{figure}
\clearpage

\clearpage
\subsection{HLT}

\clearpage
\subsection{EPT\_MISCONFIG}

\clearpage
\subsection{PREEMPTION\_TIMER}

\clearpage
\subsection{EXTERNAL\_INTERRUPT}

\clearpage
\subsection{IO\_INSTRUCTION}

\clearpage
\subsection{EOI\_INDUCED}

\clearpage
\subsection{EPT\_VIOLATION}

\clearpage
\subsection{PAUSE\_INSTRUCTION}

\clearpage
\subsection{CPUID}

\clearpage
\subsection{MSR\_READ}

@@

\chapter{Real-Time Performance Tuning}\label{cha:real-time_tuning}
\section{BIOS Configurations}
\section{Kernel Configurations} 
\section{Host OS Configurations}
\subsection{Tasks and Events}
\clearpage
\subsection{CPU governor}

@@

\noindent By changing the values of the \texttt{smp\_affinity} files of the respective IRQs, the assignment of IRQs was controlled so that they would not be handled by the isolated CPU. This reduced the interruptions caused by IRQs and the isolated CPUs were able to focus more on their assigned tasks.
\clearpage
\subsection{Real-time patch}
\clearpage
\section{QEMU-KVM Configurations}
\section{Guest OS Configurations}
\clearpage
\subsection{Tasks and Events}
\clearpage

@@

Configurations for guest OS in the real-time VM .......................................................... 13

@@

\section{VARAN}
\clearpage
\section{Robotic Application}
\clearpage

@@

\cite{pixelartSIGMATEKKompletteAutomatisierungssysteme}
\cite{Tracecmd}
\cite{KernelShark}
\cite{XenomaiXenomai}
\cite{WelcomeYoctoProject}
\cite{QEMU}
\cite{linPerformanceEvaluationXenomai}
\cite{abediRTNFPredictableLatency2019}
\cite{broskyShieldedProcessorsGuaranteeing2003}
\cite{casiniLatencyAnalysisVirtualization2021}
\cite{cinqueVirtualizingMixedCriticalitySystems2022}
\cite{garcia-vallsChallengesRealtimeVirtualization2014}
\cite{guStateoftheArtSurveyRealTime2012}
\cite{HardRealTime}
\cite{javierperezHowRealTime2022}
\cite{kirovaImpactModernVirtualization2019}
\cite{kiszkaLinuxRealTimeHypervisor}
\cite{lutsykPipelinedMulticoreMachine2020}
\cite{malallahComprehensiveStudyKernel2021}
\cite{masrurVMBasedRealTimeServices2010}
\cite{mckenneyRealTimeVs}
\cite{pielAsymmetricSchedulingLoad2006}
\cite{queirozTestingLimitsGeneralpurpose2023}
\cite{reghenzaniRealTimeLinuxKernel2020}
\cite{yoonRealTimePerformanceAnalysis}
\cite{adamPerformanceAssessmentLinux2021}
\clearpage

>>>>

\chapter{Salamander 4}\label{cha:salamander4}
This chapter briefly describes the Salamander 4 operating system by SIGMATEK.

\section{General}
\noindent Salamander 4 is the proprietary operating system of SIGMATEK. It is based on Linux version 5.15.94 and integrates Xenomai 3.2, a real-time development environment \cite{XenomaiXenomai}. Salamander 4 is a 64-bit system, which refers to the x86\_64 architecture. The real-time behaviour is achieved through the use of Symmetric Multi-Processing (SMP) and Preemptive Scheduling (PREEMPT). In addition, it uses IRQPIPE to process interrupts in a way that meets the real-time requirements of the system. The output of the command \texttt{uname -a} can be observed in code \ref{output:uname_a_virt}.

@@

\clearpage
\chapter{KVM exit reasons}\label{cha:kvm_exit_reasons}
\section{APIC\_WRITE}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/kvm_exit_vapic.png}
	\caption[kvm exits default]{kvm exits default}
	\label{fig:kvm_exit_vapic}
\end{figure}

\section{HLT}
\section{EPT\_MISCONFIG}
\section{PREEMPTION\_TIMER}
\section{EXTERNAL\_INTERRUPT}
\section{IO\_INSTRUCTION}
\section{EOI\_INDUCED}
\section{EPT\_VIOLATION}
\section{PAUSE\_INSTRUCTION}
\section{CPUID}
\section{MSR\_READ}

@@

\chapter{Real-Time Performance Tuning}\label{cha:real-time_tuning}
\section{BIOS Configurations}
\section{Kernel Configurations} 
\section{Host OS Configurations}
\subsection{Tasks and Events}
\subsection{CPU governor}

@@

\noindent By changing the values of the \texttt{smp\_affinity} files of the respective IRQs, the assignment of IRQs was controlled so that they would not be handled by the isolated CPU. This reduced the interruptions caused by IRQs and the isolated CPUs were able to focus more on their assigned tasks.

\subsection{Real-time patch}
\clearpage
\section{QEMU-KVM Configurations}
\section{Guest OS Configurations}
\clearpage

@@

@@

\section{VARAN}
\section{Robotic Application}
\clearpage

@@

\cite{pixelartSIGMATEKKompletteAutomatisierungssysteme}
\cite{Tracecmd}
\cite{KernelShark}
\cite{XenomaiXenomai}
\cite{CPUEinheitenSIGMATEK}
\cite{EngineeringToolLASAL}
\cite{WelcomeYoctoProject}
\cite{QEMU}
\cite{linPerformanceEvaluationXenomai}
\cite{broskyShieldedProcessorsGuaranteeing2003}
\cite{cinqueVirtualizingMixedCriticalitySystems2022}
\cite{garcia-vallsChallengesRealtimeVirtualization2014}
\cite{guStateoftheArtSurveyRealTime2012}
\cite{HardRealTime}
\cite{javierperezHowRealTime2022}
\cite{kirovaImpactModernVirtualization2019}
\cite{kiszkaLinuxRealTimeHypervisor}
\cite{lutsykPipelinedMulticoreMachine2020}
\cite{malallahComprehensiveStudyKernel2021}
\cite{masrurVMBasedRealTimeServices2010}
\cite{mckenneyRealTimeVs}
\cite{pielAsymmetricSchedulingLoad2006}
\cite{queirozTestingLimitsGeneralpurpose2023}
\cite{reghenzaniRealTimeLinuxKernel2020}
\cite{yoonRealTimePerformanceAnalysis}
\cite{adamPerformanceAssessmentLinux2021}
\cite{adamRealTimePerformanceResponse2021}
\cite{deoliveiraDemystifyingRealTimeLinux}
\cite{RealTimePerformanceTuning2022}
\clearpage
